|

### 2020-09-04 paper.Rmd
dot points for discussion

---
title: |
  Burning sage: Reversing the curse of dimensionality in the visualisation of high-dimensional data
type: Article
author:
  - name: Ursula Laa
    affil: a, b
    email: ursula.laa@monash.edu
  - name: Dianne Cook
    affil: b
    email: dicook@monash.edu
  - name: Stuart Lee
    affil: b, c
    email: stuart.lee1@monash.edu
affiliation:
  - num: a
    address: |
      School of Physics and Astronomy, Monash University
  - num: b
    address: |
      Department of Econometrics and Business Statistics, Monash University
  - num: c
    address: |
      Molecular Medicine Division, Walter and Eliza Hall Institute, Parkville, Australia
bibliography: biblio.bib
geometry: margin=2.5cm
abstract: |
  In high-dimensional data analysis the curse of dimensionality observes that points tend to be far away the center of the distribution on the edge of high-dimensional space. However, if the data is projected onto a lower dimensional subspace the inverse happens; projected points tend to clump at the center obscuring any resulting visualisations. We propose to reverse the curse using radial transformations of the projections obtained using the grand tour, called the burning sage algorithm. We apply our algorithm in several case studies that show how our sage visualisations enhance exploratory clustering and classification workflows.
keywords: |
  data visualisation; grand tour; statistical computing; statistical graphics; multivariate data; dynamic graphics
header-includes: |
  \usepackage{hyperref}
  \usepackage[utf8]{inputenc}
  \def\tightlist{}
  \usepackage{setspace}
output: rticles::tf_article
keep_tex: true
---

@@

@@

What other transformations on the projected data make sense?

@@

How this would be applied in practice: clustering, classification?

>>>>

---
title: |
  Burning sage: Reversing the curse of dimensionality in the visualisation of high-dimensional data
type: Article
author:
  - name: Ursula Laa
    affil: a, b
    email: ursula.laa@monash.edu
  - name: Dianne Cook
    affil: b
    email: dicook@monash.edu
  - name: Stuart Lee
    affil: b, c
    email: stuart.lee1@monash.edu
affiliation:
  - num: a
    address: |
      School of Physics and Astronomy, Monash University
  - num: b
    address: |
      Department of Econometrics and Business Statistics, Monash University
  - num: c
    address: |
      Molecular Medicine Division, Walter and Eliza Hall Institute, Parkville, Australia
bibliography: biblio.bib
geometry: margin=2.5cm
abstract: |
  In high-dimensional data analysis the curse of dimensionality observes that points tend to be far away from the center of the distribution and on the edge of high-dimensional space. However, if the data is projected onto a lower dimensional subspace the inverse happens; projected points tend to clump at the center obscuring any resulting visualisations. We propose to reverse the curse using radial transformations of the projections obtained using the grand tour, called the burning sage algorithm. We apply our algorithm in several case studies that show how our sage visualisations enhance exploratory clustering and classification workflows.
keywords: |
  data visualisation; grand tour; statistical computing; statistical graphics; multivariate data; dynamic graphics
header-includes: |
  \usepackage{hyperref}
  \usepackage[utf8]{inputenc}
  \def\tightlist{}
  \usepackage{setspace}
output: rticles::tf_article
keep_tex: true
---

@@

- better idea of size of cluster cause not bunching 
- rescale = FALSE

@@

* short summary of what you've done; introduced the sage display to 'reverse' the curse and applied it to several datasets in natural sciences and machine learning...

* pros of the proposed technique: alleviates overplotting issues,  better seperation of clusters and size of clusters; linear up to a point, point to pollen example; very quick to compute and still interpretable; point to examples here
How this would be applied in practice: clustering, classification?

* limitations of the proposed technique: finding appropriate parameters for data; acknowledge bunching but we are not able to capture what is happening - ignoring information in the high-d if you didn't rely on linear projections; possible introduces distortions point back that is also a problem for NLDR techniques but we see where it is happening

* further work or investigation: 
What other transformations on the projected data make sense?

@@
